Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-02-04 paper/main.tex
fixed table

\begin{table*}[tb]%time
  \caption{Mean fitness (and standard deviation), over 10 independent runs for each problem instance, of the best solution found at the end of each run of the original CEGO (\CEGOorig) and its improved version (\CEGOinv) and three configurations of UMM that different in the budget of evaluations $m \in \{100, 200, 400\}$. The runs of CEGO used a budget of $m=400$.\label{tab:results_fitness}}
\begin{tabular}{llrrrrr}
\toprule
\bf Problem & \bf   Instance &  \CEGOinv &  \CEGOorig &  UMM$_{400}$ &   UMM$_{200}$ &  UMM$_{100}$ \\
\midrule
    LOP &    N-p40-01 &   1195.90 &    1170.81 &     3.12 &  0.850000 &     0.21 \\
    LOP &    N-p40-02 &   1207.24 &    1183.09 &     3.11 &  0.830000 &     0.20 \\
    LOP &  N-t59b11xx &   1265.98 &    1240.36 &     3.78 &  0.950000 &     0.23 \\
    LOP &  N-t59d11xx &   1269.93 &    1252.89 &     3.93 &  0.966667 &     0.25 \\
    LOP &  N-sgb75.01 &   1994.22 &    2004.70 &    10.88 &  2.730000 &     0.72 \\
    LOP &  N-sgb75.02 &   1995.09 &    1975.41 &    10.88 &  2.760000 &     0.69 \\
   PFSP &       rec05 &   1099.63 &     917.81 &     0.80 &  0.200000 &     0.10 \\
   PFSP &       rec13 &   1109.51 &    1043.08 &     0.85 &  0.200000 &     0.10 \\
   PFSP &       rec19 &   1090.06 &    1087.38 &     1.76 &  0.470000 &     0.10 \\
   PFSP &       rec31 &   1387.09 &    1367.26 &     4.77 &  1.280000 &     0.32 \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[tb]%fitness
\begin{tabular}{llrrrrr}
\toprule
Problem &    Instance &   \CEGOinv &  \CEGOorig &    UMM$_{400}$ &       UMM$_{200}$ &    UMM$_{100}$ \\
\midrule
    LOP &    N-p40-01 &    10496.6 &    15027.7 &    12453.7 &  1.336170e+04 &    14649.9 \\
    LOP &    N-p40-02 &    11714.7 &    15150.2 &    13191.9 &  1.420900e+04 &    15206.2 \\
    LOP &  N-t59b11xx &   102408.0 &   126204.0 &   114726.5 &  1.202020e+05 &   132039.5 \\
    LOP &  N-t59d11xx &    12692.2 &    30199.8 &    16775.4 &  2.352089e+04 &    29884.1 \\
    LOP &  N-sgb75.01 &  1893533.2 &  2095899.6 &  1983521.2 &  2.004006e+06 &  2046895.1 \\
    LOP &  N-sgb75.02 &  1895801.8 &  2069286.9 &  1973083.9 &  2.001244e+06 &  2039356.1 \\
   PFSP &       rec05 &     1276.2 &     1318.7 &     1282.1 &  1.287000e+03 &     1320.2 \\
   PFSP &       rec13 &     1992.9 &     2096.0 &     2077.7 &  2.108500e+03 &     2131.6 \\
   PFSP &       rec19 &     2264.5 &     2328.4 &     2318.5 &  2.352100e+03 &     2386.5 \\
   PFSP &       rec31 &     3415.5 &     3512.3 &     3420.5 &  3.490900e+03 &     3474.3 \\
\bottomrule
\end{tabular}\end{table*}

>>>>

\begin{table*}[tb]%time
  \caption{Mean runtime  in minutes, over 10 independent runs for each problem instance, of the original CEGO (\CEGOorig) and its improved version (\CEGOinv) and three configurations of UMM that differ in the budget of evaluations $m \in \{100, 200, 400\}$. The runs of CEGO used a budget of $m=400$.\label{tab:results_time}}
\begin{tabular}{llrrrrr}
\toprule
\bf Problem & \bf   Instance &  \CEGOinv &  \CEGOorig &  UMM$_{400}$ &   UMM$_{200}$ &  UMM$_{100}$ \\
\midrule
    LOP &    N-p40-01 &   1195.90 &    1170.81 &     3.12 &  0.850000 &     0.21 \\
    LOP &    N-p40-02 &   1207.24 &    1183.09 &     3.11 &  0.830000 &     0.20 \\
    LOP &  N-t59b11xx &   1265.98 &    1240.36 &     3.78 &  0.950000 &     0.23 \\
    LOP &  N-t59d11xx &   1269.93 &    1252.89 &     3.93 &  0.966667 &     0.25 \\
    LOP &  N-sgb75.01 &   1994.22 &    2004.70 &    10.88 &  2.730000 &     0.72 \\
    LOP &  N-sgb75.02 &   1995.09 &    1975.41 &    10.88 &  2.760000 &     0.69 \\
   PFSP &       rec05 &   1099.63 &     917.81 &     0.80 &  0.200000 &     0.10 \\
   PFSP &       rec13 &   1109.51 &    1043.08 &     0.85 &  0.200000 &     0.10 \\
   PFSP &       rec19 &   1090.06 &    1087.38 &     1.76 &  0.470000 &     0.10 \\
   PFSP &       rec31 &   1387.09 &    1367.26 &     4.77 &  1.280000 &     0.32 \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[tb]%fitness
    \caption{Mean fitness, over 10 independent runs for each problem instance, of the best solution found at the end of each run of the original CEGO (\CEGOorig) and its improved version (\CEGOinv) and three configurations of UMM that differ in the budget of evaluations $m \in \{100, 200, 400\}$. The runs of CEGO used a budget of $m=400$.\label{tab:results_fitness}}
\begin{tabular}{llrrrrr}
\toprule
Problem &    Instance &   \CEGOinv &  \CEGOorig &    UMM$_{400}$ &       UMM$_{200}$ &    UMM$_{100}$ \\
\midrule
    LOP &    N-p40-01 &    10496.6 &    15027.7 &    12453.7 &  1.336170e+04 &    14649.9 \\
    LOP &    N-p40-02 &    11714.7 &    15150.2 &    13191.9 &  1.420900e+04 &    15206.2 \\
    LOP &  N-t59b11xx &   102408.0 &   126204.0 &   114726.5 &  1.202020e+05 &   132039.5 \\
    LOP &  N-t59d11xx &    12692.2 &    30199.8 &    16775.4 &  2.352089e+04 &    29884.1 \\
    LOP &  N-sgb75.01 &  1893533.2 &  2095899.6 &  1983521.2 &  2.004006e+06 &  2046895.1 \\
    LOP &  N-sgb75.02 &  1895801.8 &  2069286.9 &  1973083.9 &  2.001244e+06 &  2039356.1 \\
   PFSP &       rec05 &     1276.2 &     1318.7 &     1282.1 &  1.287000e+03 &     1320.2 \\
   PFSP &       rec13 &     1992.9 &     2096.0 &     2077.7 &  2.108500e+03 &     2131.6 \\
   PFSP &       rec19 &     2264.5 &     2328.4 &     2318.5 &  2.352100e+03 &     2386.5 \\
   PFSP &       rec31 &     3415.5 &     3512.3 &     3420.5 &  3.490900e+03 &     3474.3 \\
\bottomrule
\end{tabular}\end{table*}
